Painting with Triangles

### 2014-06-06 paper.tex
Changed modified to be not green. Changed the word render to process in the graph and text.

\subsection{Complexity}
To find the growth rates of the algorithm we performed two experiments. 
First, the program drew fifty random strokes without zooming.
Next, the program drew fifty random strokes with random zoom level for each stroke.
Geometry grows fastest when many strokes are composited on one another. When not zooming, strokes
must cover the same area of canvas over and over. This
results in more geometry and therefore takes longer to \modified{process this new stroke}. The zooming case explores different
areas of the canvas and therefore results in less overlapping geometry. This situation should result
in less complex geometry and therefore take less time.

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % \includegraphics[width=\columnwidth]{graphs/numtriangles}
    \includegraphics[height=1.2in]{graphs/numtriangles}
    \caption{Number of triangles}
    \label{fig:numtriangles}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % \includegraphics[width=\columnwidth]{graphs/cumulativetime}
    \includegraphics[height=1.2in]{graphs/cumulativetime}
    \caption{Processing time}
    \label{fig:timing}
  \end{subfigure}%
  \caption{For paintings of 50 random strokes, the left graph shows the number of triangles in the canvas as of stroke $x$, and the right graph shows the cumulative process time of the painting. The blue points are the non-zooming case, while the red points are the zooming case.}
\end{figure}

>>>>

\subsection{Complexity}
To find the growth rates of the algorithm we performed two experiments. 
First, the program drew fifty random strokes without zooming.
Next, the program drew fifty random strokes with random zoom level for each stroke.
Geometry grows fastest when many strokes are composited on one another. When not zooming, strokes
must cover the same area of canvas over and over. This
results in more geometry and therefore takes longer to \modified{process}. The zooming case explores different
areas of the canvas and therefore results in less overlapping geometry. This situation should result
in less complex geometry and therefore take less time.

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % \includegraphics[width=\columnwidth]{graphs/numtriangles}
    \includegraphics[height=1.2in]{graphs/numtriangles}
    \caption{Number of triangles}
    \label{fig:numtriangles}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % \includegraphics[width=\columnwidth]{graphs/cumulativetime}
    \includegraphics[height=1.2in]{graphs/cumulativetime}
    \caption{Processing time}
    \label{fig:timing}
  \end{subfigure}%
  \caption{For paintings of 50 random strokes, the left graph shows the number of triangles in the canvas as of stroke $x$, and the right graph shows the cumulative processing time of the painting. The blue points are the non-zooming case, while the red points are the zooming case.}
\end{figure}
